Spherical harmonic analysis of faceted spheroids identifies shaping strategies and standardisation at Qianshangying (North China)

### 2025-09-19 analysis/paper/paper.qmd
update of funding and credit authorship

Ye Zhi: Writing – review & editing, Writing – original draft, Visualization, Resources, Project administration, Methodology, Investigation, Funding acquisition, Formal analysis, Data curation, Conceptualization. Ben Marwick: Writing – original draft, review & editing, Supervision, Project administration, Methodology, Conceptualization. Li Hao: Writing – review & editing, Conceptualization, Funding acquisition. Shuwen Pei: Writing – review & editing, Conceptualization, Funding acquisition.

@@

This work was financially supported through the ...

>>>>

Ye Zhi: Writing – review & editing, Writing – original draft, Visualization, Resources, Project administration, Methodology, Investigation, Funding acquisition, Formal analysis, Data curation, Conceptualization. Shuwen Pei: Writing – review & editing, Supervision, Conceptualization, Funding acquisition. Dongdong Ma: Formal analysis, Data curation. Hao Li: Writing – review & editing, Conceptualization. Ben Marwick: Writing – original draft, review & editing, Supervision, Project administration, Methodology, Conceptualization.

@@

This work was financially supported through the National Natural Foundation of China (Grant No. 42371165), Please list foundation from Ben, and China Scholarship Council Programme for international student (CSC No. 202404910542)
